Offline Mode for Corporate Mobile Client Security Architecture

### 2017-01-10 docs/papers/2016MONE/2016MONE.tex
correcoes do prof rafael e adicao de referencias recomendadas

\author{Tatiana Galibus				\and
        Thiago P. de B. Vieira		\and
        	Edison P. de Freitas			\and
        	Robson O. Albuquerque		\and
        	João Paulo C. L da Costa		\and
        	Rafael T. de Sousa Júnior	\and
        Viktor Krasnoproshin			\and
        	Anton Zaleski				\and
        	H.E.R.M. Vissia				\and
        	Giovanni del Galdo
}

\institute{Tatiana Galibus \and Viktor Krasnoproshin \at
              Belarusian State University, Minsk, 4, Nezavisimosti, 220030, Belarus
           \and
           Tatiana Galibus \and Thiago P. B. Vieira \and Robson O. Albuquerque \and João Paulo C. L da Costa \and Rafael T. de Sousa Júnior  \at
              University of Brasilia, UnB, FT, ENE, CP: 4386, 70910-900, Brasília, Brazil
           \and
           Edison P. de Freitas \at
				Federal University of Rio Grande do Sul, UFRGS, INF, CP: 15064, 91501-970, Porto Alegre, Brazil
           \and
           João Paulo C. L da Costa \and Giovanni del Galdo \at
				Institute for Information Technology, Ilmenau University of Technology, Ilmenau, Germany
           \and
           João Paulo C. L da Costa \and Giovanni del Galdo \at
				Fraunhofer Institute for Integrated Circuits IIS, Erlangen, Germany
           \and
           Anton Zaleski \and H.E.R.M. Vissia \at
				Byelex Multimedia Products BV Argon 1, 4751 XC Oud Gastel, The Netherlands
}

@@

\begin{abstract}
Preventing data leakage on the mobile client is a crucial security problem. Therefore, additional control and protection should be taken for the confidential data on the mobile clients that leave the boundaries of the organization. In this scenario, such apps can be used on the offline mode for the convenience and traffic reducing or even for a particular characteristic of the mobile client or of the business. This paper presents a novel approach to the security of the corporate mobile clients, in particular the offline mode. The important part of the presented approach is the conceptualization and the definition of the core methodology to solve the problem of offline mobile security, i.e. the protection of the confidential data in use when the mobile client is not connected to the corporate cloud. The protection of the sensitive data is provided by the combination of the cryptographic and analytics methods to detect malicious user behavior. The proposed security architecture supports the basic mobile client protection principles: minimized traffic load and reduced communication with the cloud; usage of the light-weighted operations and an optimized combination of the security methods.
\end{abstract}

\keywords{ offline mobile cloud security \and offline attribute-based encryption \and model order selection \and user behavior analysis \and secret sharing}

@@

Additional security issues and requirements have to be considered when mobile clients are actively used in corporate cloud environment \cite{yovel2014}. Today more and more organizations and enterprises are functioning in the Bring-Your-Own-Device (BYOD) paradigm. The uncontrolled usage of the mobile devices represents a serious risk to the development of secure SME cloud platforms being the bottleneck of the corporate information security system (ISS). While the enterprise cloud infrastructure based on the web interface can be protected by powerful third-party services, such as CASB and CAC, the corporate mobile client is usually light-weighted and generally less protected. The protection scheme used on a mobile device should be both computationally secure as well as resource-constrained due to battery power limitations \cite{khan2015cloud}. Therefore, encrypting files and generating keys on a mobile device is not considered a good solution. On the other hand, the protection schemes with good computational qualities lack the security analysis in many cases \cite{khan2014bss}. The common practice is the shadow user activities monitoring \cite{yovel2014}. However, the mobile device usage stays unprotected in all the proposed scenarios while in offline mode.

@@

From the theoretical point of view of this problem, there are several surveys, whose common point is the mobile cloud as a rapidly developing paradigm that poses many security and complexity problems \cite{yovel2014, khan2015cloud, khan2014survey, khan2013towards}. An analysis of the new models of mobile cloud computing and new ways of using data storage services is presented in \cite{khan2015cloud, khan2013towards}. Commonly, all the models and protection schemes concentrate on the encryption properties and either perform the computations on their own \cite{zhao2010trusted, yang2011provable} or use the cloud provider to off-load the cryptographic operations \cite{itani2010energy, ren2011lightweight}. Obviously, it is natural the mobile client cannot handle all operations securely without the assistance of a cloud provider, due to resources constraint and battery limitation.

The necessity to use schemes that function without putting load on a provider arises when it is desired to make the mobile client less dependent on the cloud provider, i.e. corporate client continues to provide the secure access to the sensitive data without connection to the network. As discussed in \cite{khan2015cloud}, all the currently known schemes of encryption, performing the computation, either use a cloud provider \cite{zhao2010trusted}, a third party trusted agent \cite{yang2011provable} or a combination of both \cite{itani2010energy}. In some cases, they concentrate on computational complexity without taking care of user privacy and security \cite{ren2011lightweight}.
Therefore, according to \cite{khan2015cloud, tenorio2013greatest, khan2013towards}, the state-of-the-art mobile cloud security models do not consider the problem of the offline security mode.

@@

\section{The mobile security architecture}
\label{sec_the_client_security_architecture}
The approach proposed in this work describes and implements the complete lifecycle of the mobile client security infrastructure. The mobile security processes depend on the key expiry period, and are used to access the protected storage. Once the user keys expire, the user is requested to enter his valid credentials, i.e. PIN and password. The mobile client then sends the credentials to the server for verification. Once the new set of access keys is received, the user can access the protected files in the offline mode, without the access to the server. This means that no further communication with the server is needed until the key expires. The core set of functions and protocols can be divided into three sets of operations as shown in Figure \ref{fig:01}.

@@

\begin{acknowledgements}
The authors thank the Brazilian research and innovation agencies FAPDF (Research Support Foundation of the Federal District), FINEP (Agreement RENASIC / PROTO 01.12.0555.00), CAPES and CNPq under the FORTE Project - CAPES Forensic Sciences Announcement 25/2014, under the productivity grant number 303905 / 2014-0, under the PVE project number 88881.030392 / 2013-01 for their financial support on this research, and under the project number 207644/2015-2 for the PDE scholarship in the context of the program CSF - Aerospace Technology.\end{acknowledgements}

>>>>

\author{Tatiana Galibus				\and
        Thiago P. de B. Vieira		\and
        	Edison P. de Freitas			\and
        	Robson de O. Albuquerque		\and
        	João Paulo C. L da Costa		\and
        	Rafael T. de Sousa Júnior	\and
        Viktor Krasnoproshin			\and
        	Anton Zaleski				\and
        	H.E.R.M. Vissia				\and
        	Giovanni del Galdo
}

\institute{Tatiana Galibus \and Viktor Krasnoproshin \at
              Belarusian State University, Minsk, 4, Nezavisimosti, 220030, Belarus
           \and
           Tatiana Galibus \and Thiago P. de B. Vieira \and Robson de O. Albuquerque \and João Paulo C. L da Costa \and Rafael T. de Sousa Júnior  \at
              University of Brasilia, UnB, FT, ENE, CP: 4386, 70910-900, Brasília, Brazil
           \and
           Edison P. de Freitas \at
				Federal University of Rio Grande do Sul, UFRGS, INF, CP: 15064, 91501-970, Porto Alegre, Brazil
           \and
           João Paulo C. L da Costa \and Giovanni del Galdo \at
				Institute for Information Technology, Ilmenau University of Technology, Ilmenau, Germany, and Fraunhofer Institute for Integrated Circuits IIS, Erlangen, Germany
           \and
           Anton Zaleski \and H.E.R.M. Vissia \at
				Byelex Multimedia Products BV Argon 1, 4751 XC Oud Gastel, The Netherlands
}

@@

\begin{abstract}
Preventing data leakage on the mobile client is a crucial security problem. Therefore, additional control and protection should be taken for the confidential data on the mobile clients that leave the boundaries of the organization. This paper presents a novel approach to the security of the corporate mobile clients, in particular when they operate in the offline mode. The presented approach includes the essential conceptualization and the definition of the core methodology to solve the problem of offline mobile security, i.e. the protection of the confidential data in use when the mobile client is not connected to the corporate cloud. The protection of the sensitive data is provided by the combination of cryptographic means and analytics methods to detect malicious user behavior. The proposed security architecture supports the basic mobile client protection principles: minimized traffic load and reduced communication with the cloud; usage of light-weighted operations and an optimized combination of the security methods.
\end{abstract}

\keywords{offline mobile cloud security \and offline attribute-based encryption \and model order selection \and user behavior analysis \and secret sharing}

@@

Additional security issues and requirements have to be considered when mobile clients are actively used in corporate cloud environment \cite{yovel2014}. Today more and more organizations and enterprises are functioning in the Bring-Your-Own-Device (BYOD) paradigm. The uncontrolled usage of the mobile devices represents a serious risk to the development of secure SME cloud platforms being the bottleneck of the corporate information security system (ISS). While the enterprise cloud infrastructure based on the web interface can be protected by powerful third-party services, such as CASB and CAC, the corporate mobile client is usually light-weighted and generally less protected.

The protection scheme used on a mobile device should be both computationally secure as well as resource-constrained due to battery power limitations \cite{khan2015cloud}. Therefore, encrypting files and generating keys on a mobile device is not considered a good solution. On the other hand, the protection schemes with good computational qualities lack the security analysis in many cases \cite{khan2014bss}. The common practice is the shadow user activities monitoring \cite{yovel2014}. However, the mobile device usage stays unprotected in all the proposed scenarios while in offline mode.

@@

From the theoretical point of view of this problem, there are several surveys, whose common point is the mobile cloud as a rapidly developing paradigm that poses many security and complexity problems \cite{khan2013towards, yovel2014, khan2014survey, khan2015cloud, mayrhofer2015architecture, chang2015design, xia2015tinman, kulkarni2015addressing, shila2016amcloud, heydari2016efficient}. Kulkarni and Khanai \cite{kulkarni2015addressing} discuss the most important threats related to Mobile Cloud Computing and argue that there is a need for a lightweight secure framework that provides security with minimum communication and processing overhead on mobile devices.

An analysis of the new models of mobile cloud computing and new ways of using data storage services is presented in \cite{khan2015cloud, khan2013towards, mayrhofer2015architecture, chang2015design}. Commonly, the models and protection schemes concentrate on the encryption properties and either perform the computations on their own \cite{zhao2010trusted, yang2011provable} or use the cloud provider to off-load the cryptographic operations \cite{itani2010energy, ren2011lightweight}. Obviously, it is natural the mobile client cannot handle all operations securely without the assistance of a cloud provider, due to resources constraint and battery limitation.

The necessity to use schemes that function without putting load on a provider arises when it is desired to make the mobile client less dependent on the cloud provider, i.e. corporate client continues to provide the secure access to the sensitive data without connection to the network. As discussed in \cite{khan2015cloud}, all the currently known schemes of encryption, performing the computation, either use a cloud provider \cite{zhao2010trusted}, a third party trusted agent \cite{yang2011provable, heydari2016efficient}, a combination of both \cite{itani2010energy} or ad hoc approaches \cite{shila2016amcloud}. In some cases, they concentrate on computational complexity without taking care of user privacy and security \cite{ren2011lightweight}. Therefore, according to \cite{khan2013towards, khan2015cloud}, the state-of-the-art mobile cloud security models do not consider the problem of the offline security mode.

@@

\section{The mobile security architecture}
\label{sec_the_client_security_architecture}
The approach proposed in this work describes and implements the complete lifecycle of the mobile client security infrastructure. The mobile security processes depend on the key expiry period, and are used to access the protected storage. Once the user keys expire, the user is requested to enter his valid credentials, i.e. PIN and password. The mobile client then sends the credentials to the server for verification. Once the new set of access keys is received, the user can access the protected files in the offline mode, without the access to the server. This means that no further communication with the server is needed until the key expires.

The core set of functions and protocols can be divided into three sets of operations as shown in Figure \ref{fig:01}.

@@

\begin{acknowledgements}
The authors thank the Brazilian research and innovation agencies CAPES (Grant FORTE \\23038.007604/2014-69), FAPDF (Research Support Foundation of the Federal District), FINEP (Grant RENASIC PROTO 01.12.0555.00), CNPq (Productivity grant 303905/2014-0 and PVE Grant 88881.030392/2013-01), as well as the European CSF - Aerospace Technology Program (PDE scholarship within project 207644/2015-2), for their support to this research.\end{acknowledgements}
